A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD, by Interpolating in the Principal Component Spaces

### 2018-03-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex

>>>>

Four upscaled models were obtained from a base case which is a high-resolution permeability field with a known permeability distribution. The base case consists of four regions, where each region is uniformly randomly generated within a specified range. For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate. Newmann ({\it i.e.} no flux) boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face. Fig (...........)a shows the permeability field of the base case while fig
